BlogForever Crawler: Techniques and Algorithms to Harvest Modern Weblogs

### 2013-11-20 tex/3-algorithms.tex
up

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction rules and string similarity}
% XPath selectors (id, else class, else path)
In our implementation, rules are queries in the XML Path Language (XPath). Consequently, standard libraries can be used parse html pages and apply extraction rules, thus providing the \code{apply} function use Algorithm \ref{extractionAlgo}. We experimented with 3 types of XPath queries: selection over \code{id} attribute, selection over \code{class} attribute and selection with absolute path. We have found that ignoring nodes without \code{id} or \code{class} absolutes prunes out a lot of uninteresting HTML nodes without decreasing  the quality of the result. Also when both \code{id} and \code{class} attributes are present the \code{id} attribute shows to be a stronger selector, here matching the HTML specification regarding the uniqueness of \code{id}. This observations led to the following \code{\ref{allrulesAlgo}} function:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Linear time reformulation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Variations for comments, date and authors extraction}
- comments
- date authors

>>>>

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction rules and string similarity}
% XPath selectors (id, else class, else path)
In our implementation, rules are queries in the XML Path Language (XPath). Consequently, standard libraries can be used parse html pages and apply extraction rules, thus providing the \code{apply} function use Algorithm \ref{extractionAlgo}. We experimented with 3 types of XPath queries: selection over \code{id} attribute, selection over \code{class} attribute and selection with absolute path. We have found that ignoring nodes without \code{id} or \code{class} absolutes prunes out a lot of uninteresting HTML nodes without decreasing  the quality of the result. Also when both \code{id} and \code{class} attributes are present the \code{id} attribute shows to be a stronger selector, here matching the HTML specification regarding the uniqueness of \code{id}. This observations led to the following \code{\ref{allrulesAlgo}} function:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time complexity, linear reformulation}

We will now show that Algorithm \ref{extractionAlgo} has a quadratic running time. Let's first assume that we have at our disposal a linera time HTML parser that build an index on

As stated before, the outer simply splits the input into independent computations. \ref{allrulesAlgo} return a lkajsd flkasjd félkasjd félaksdjfélaskdjf
% Algo 1 is quadratic

% Linera reformulation

% Algo 2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Variations for comments and authors}
- comments
- date authors
